Dark matter halo shape in the Auriga simulations: radial dependence, time evolution and correlation with baryon disk properties

### 2019-07-17 Document/paper.tex
caption paper 2

\title[The shape of dark matter haloes in the Auriga simulations]
{Dark matter halo shape in the Auriga simulations: radial
  dependence, time evolution and correlation with baryon disk
  properties}
\author[Jesus Prada,  Jaime E. Forero-Romero, Volker Springel ]{
Jesus Prada,$^{1}$\thanks{E-mail: jd.prada1760@uniandes.edu.co}
Jaime E. Forero-Romero,$^{1}$
Volker Springel$^{2}$
\\
% List of institutions
$^{1}$Departamento de F\'sica, Universidad de los Andes, Cra. 1 No.
18A-10, Edificio Ip, Bogot\'a, Colombia.\\
$^{2}$Heidelberg Institute for Theoretical Studies, Schloss-Wolfsbrunnenweg 35, D-69118 Heidelberg
paperGermany.\\
}

@@

\begin{figure*}
\begin{center}
\includegraphics[width=0.9\columnwidth]{Lvl_4_Triax_Plane_DM.pdf}
 \includegraphics[width=0.9\columnwidth]{Lvl_4_Triax_Plane_MHD.pdf}
\end{center}
\caption{Axial ratios for the 30 halos in the Level 3 DM simulations
  on the left and MHD simulations on the right.
   Each dot represents the shape characterization of each halo 
   Red circles represent measurements at the virial radius and the
   blue squares are measurements at 1/8 of the virial radius.   
   The crosses represent the mean values and standard deviation of
   each sample.
   Overall we can see three things. 
   First, in DM only simulations halos are rounder in the outskirts
   than in the inner part.
   Second, halos in MHD are rounder than its DM only counterparts.
   Third, halos in MHD simulations are slightly rounder in the inner
   part compared to the outskirts.}
  \label{fig:triaxiality_plane}
\end{figure*}

\begin{figure*}
\includegraphics[width=0.9\columnwidth]{triaxialiy_distro_DM.pdf}
\includegraphics[width=0.9\columnwidth]{triaxialiy_distro_MHD.pdf}
\caption{Cumulative fraction of the triaxiality for all 30 halos in
  Level 4 simulations. Right/left panel correspond to DM/MHD
  simulations respectively. 
  This quantifies the main trends we find: in DM only simulations
  rounder in the outskirts, halos in MHD are rounder than DM only, and
  in MHD simulations halos tend to be rounder at the inner regions
  than its outskirts.}
\label{fig:triaxial_cumulative}
\end{figure*}

>>>>

\title[The shape of dark matter haloes in the Auriga simulations]
{Dark matter halo shape in the Auriga simulations: radial
  dependence, time evolution and correlation with baryon disk
  properties}
\author[Jesus Prada,  Jaime E. Forero-Romero, Volker Springel ]{
Jesus Prada,$^{1}$\thanks{E-mail: jd.prada1760@uniandes.edu.co}
Jaime E. Forero-Romero,$^{1}$
Volker Springel$^{2}$
\\
% List of institutions
$^{1}$Departamento de F\'sica, Universidad de los Andes, Cra. 1 No.
18A-10, Edificio Ip, Bogot\'a, Colombia.\\
$^{2}$Heidelberg Institute for Theoretical Studies,
Schloss-Wolfsbrunnenweg 35, D-69118 Heidelberg, Germany.\\
}

@@

\begin{figure*}
\begin{center}
\subfloat[DMO simulations.]{\includegraphics[width=0.9\columnwidth]{Lvl_4_Triax_Plane_DM.pdf}}
\subfloat[MHD simulations.]{\includegraphics[width=0.9\columnwidth]{Lvl_4_Triax_Plane_MHD.pdf}}
\end{center}
\caption{Axial ratios for all halos in the simulation.
  Left/right panels correspond to DMO/MHD simulations, respectively.
  Triangles (squares) represent the measurements at $R_{200}/16$
  ($R_{200}$) which correspond to physical distances of $14\pm 1$ kpc
  ($230\pm 15$ kpc) respectively.
  Here we can visualize three main trends for the whole halo population.
  First, in DMO simulations halos are rounder in the outskirts
  than in the inner part.
  Second, halos in MHD are rounder than its DMO counterparts.
  Third, halos in MHD are less triaxial in the inner regions than in
  the outskirts}
  \label{fig:triaxiality_plane}
\end{figure*}

\begin{figure*}
\subfloat[DMO simulations.]{\includegraphics[width=0.9\columnwidth]{triaxialiy_distro_DM.pdf}}
\subfloat[MHD simulations.]{\includegraphics[width=0.9\columnwidth]{triaxialiy_distro_MHD.pdf}}
\caption{Cumulative fraction for the triaxiality at five different radii.
  Right/left panel correspond to DM/MHD
  simulations respectively. 
  This quantifies the main trends we find: in DM only simulations
  rounder in the outskirts, halos in MHD are rounder than DM only, and
  in MHD simulations halos tend to be rounder at the inner regions
  than its outskirts.}
\label{fig:triaxial_cumulative}
\end{figure*}
